A comparison of classification algorithms applied to the Adult Database

### 2009-12-16 demo/demo.tex
added ID3 slide.

>>>>

\subsection{ID3}
\frame
{
    \frametitle{ID3}

    \begin{itemize}
        \item ID3 in RapidMiner is implemented in two different flavours: one that supports numerical values, one that doesn't.
        \item An absolute discretization was conducted on numerical values for the version that doesn't support them.
        \item RapidMiner supports different splitting criterions: Gain Ratio, Information Gain, Gini Index or Accuracy.
    \end{itemize}

\footnotesize
\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c | c |}
    \hline
    \textbf{Type} & \textbf{Criterion} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    ID3 & Gain Ratio & 18.38 & 18.61 & 0m04s \\ \hline
    ID3 & Information Gain & 18.48 & 19.05 & 0m03s \\ \hline
    ID3 & Gini Index & 18.94 & 19.15 & 0m04s \\ \hline
    ID3 & Accuracy & 20.41 & 20.24 & 0m04s \\ \hline
    ID3 Numerical & Gain Ratio & 14.93 & 15.68 & 0m14s \\ \hline
    ID3 Numerical & Information Gain & 15.68 & 16.42 & 0m06s \\ \hline
    ID3 Numerical & Gini Index & 16.10 & 16.96 & 0m07s \\ \hline
    ID3 Numerical & Accuracy & 17.99 & 17.92 & 0m12s \\ \hline
  \end{tabular}
  \end{center}
\end{table}
\normalsize
}
